Digital History in Finland, 1488-1828

### 2016-06-22 inst/examples/manuscript-krakow.Rmd
Rmd update

>>>>

The publishing of historical works in .. on a timeline highlighting the eras of the riksdagar (16..-16..)..

```{r valtiopaivat, echo=FALSE, warning=FALSE, fig.width=11, fig.height=4}
# Use timeinterval year intervals
dfsel = df0
#dfsel = subset(df0, publication_place == "Stockholm")
#dfsel = subset(df0, publication_place == "Norrköping")
#dfsel = subset(df0, publication_place == "Gävle")

df <- subset(dfsel, publication_year >= 1700 & publication_year < 1800 )

timeinterval <- 1
df$timeunit <- round(df$publication_year/timeinterval)*timeinterval

df$unity = rep(1, nrow(df))
publications <- tapply(df$unity, list(df$timeunit), sum)

publications[is.na(publications)] <- 0 # Set NAs to 0
publications <- publications/timeinterval # Instead of decadal sum, use average annual output 
dfm <- melt(publications) 
names(dfm) <- c("Time", "Documents")
dfm <- transform(dfm, date = as.numeric(as.character(Time)))
ymin = min(dfm$Documents)
ymax = max(dfm$Documents)

rect_left <- c(min(na.omit(dfm$date)),
               1719-.5, 1719+.5, # Stockholm 20 januari 1719 1 juni 1719
               1734-.5, 1734+.5, # Stockholm 14 maj 1734 14 december 1734
               1765-.5, 1766+.5, # Stockholm 21 februari 1765 21 oktober 1766
               1769-.5, 1770+.5, # Norrköping & Stockholm 22 april 1769 5 februari 1770
               1771-.5, 1772+.5, # Stockholm 19 juni 1771 12 september 1772
               1792-.5, 1792+.5, # Gävle 26 januari 1792 24 februari 1792	       
               max(na.omit(dfm$date)))
  rectangles <- data.frame(
    xmin = rect_left[-length(rect_left)],
    xmax = rect_left[-1],
    ymin = ymin,
    ymax = ymax
    )
  rectangles$shade <- rep(c("White", "Highlight"), length = nrow(rectangles))
  #rectangles$shade <- rep(c("White", "Highlight"), length = nrow(rectangles))

 riksplace = c("Stockholm", "Stockholm", "Stockholm", "Norrköping", "Stockholm", "Gävle")
 cols = c("gray", "lightblue", "yellow", "white")
 rectangles$shade[rectangles$shade == "Highlight"] = riksplace
 rectangles$shade = factor(rectangles$shade)

# Draw Figure
theme_set(theme_bw(20))
p <- ggplot()
p <- p + geom_rect(data = rectangles, 
	   aes(xmin=xmin, xmax=xmax, ymin=ymin, ymax=ymax, fill=shade), alpha=0.8) + 
         scale_fill_manual(values = cols) # + guides(fill = "none") 
p <- p + geom_line(data = dfm, aes(x = date, y = Documents), col = "black")
p <- p + geom_point(data = dfm, aes(x = date, y = Documents), col = "black")
p <- p + scale_x_continuous(breaks=seq(min(dfm$date), max(dfm$date), 20))
p <- p + ggtitle("Publishing activity")
p <- p + ylab("Documents / Year")
p <- p + xlab("Year")
p <- p + ggtitle("Riksdagar - overall titlecount (Fen + Kun)")
print(p)
```
